---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
op <- options(warn = -1)

```

# seaice.map

<!-- badges: start -->
<!-- [![R-CMD-check](https://github.com/mdsumner/seaice.map/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mdsumner/seaice.map/actions/workflows/R-CMD-check.yaml)-->
<!-- badges: end -->

The goal of seaice.map is to ... display this image. 


```{r example, fig.dim = c(7, 16.8), results="hide"}
library(terra)
r <- rast("data-raw/seaice.png")
plot(r, axes = F)
points(terra::project(do.call(cbind, maps::map(plot = F)[1:2]), to = terra::crs(r), from = "OGC:CRS84"), pch = ".", col = "#777777")
title(readLines("data-raw/latestdate.txt"))

aadcgeoserver <- "WFS:https://data.aad.gov.au/geoserver/ows?service=wfs&version=2.0.0&request=GetCapabilities"
info <- vapour::vapour_layer_info(aadcgeoserver, "underway:underway")

#dat <- vapour::vapour_read_fields(aadcgeoserver, skip_n = info$count  - 24 * 60 * 5, 
#                                  sql = "SELECT date_time_utc FROM \"underway:underway\"")
geom <- vapour::vapour_read_geometry(aadcgeoserver, skip_n = info$count  - 24 * 60 * 5, 
                                  sql = "SELECT date_time_utc FROM \"underway:underway\"")
track <- wk::wk_coords(wk::wkb(geom))[, c("x", "y")]

track <- terra::project(track, to = terra::crs(r), from = "OGC:CRS84")
lines(track, col = "hotpink")
pt <- tail(track[!is.na(track[,1]) & !is.na(track[,2]), ], 1L)
points(pt, pch = "+", col = "hotpink")

```


This is 25km sea ice concentration from NSIDC, reprojected from images published by NOAA at https://noaadata.apps.nsidc.org/NOAA/G02135/ (the projection is Transverse Mercator with central longitude 147). 

The point (and track if available) is the recent position of the Nuyina vessel. 

Files in 'data-raw/' contain the actual metadata and scripts. This runs as a daily task on github actions. 

## Code of Conduct
  
Please note that the seaice.map project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
